Efficient Handling of String-Number Conversion

### 2019-11-21 evaluation.tex
Update table
Update tables, add checkLuhn graph

\begin{table}[h]
\centering
\caption{Results of Z3-Trau, CVC4, and Z3 on Basic String Constraint benchmarks (numbers with * will be updated later)}
\scalebox{0.7}{
\begin{tabular}{|l r | r r r r r r r|}
\hline
\multicolumn{2}{|c}{}                   & {\tool} & CVC4  &Z3 & Z3-str3 & Trau+ & ABC & Ostrich \\ \hline
\multirow{3}{*}{PyEx}		& sat      & 19586*   & 19763* & 18359 &   3024*  & 19149 & 0 & 111 \\ 
							& unsat    &  3858*   &  3834* &  3851 &   3839*  & 3828 & 0 & 871 \\
							& $\times$ &  1977*   &  1824* &  3211 &  18558*  & 2444 & 25421 & 24439 \\ \hline
\multirow{3}{*}{APLAS}		& sat      &   128*   &   205* &    19 &     38*  & 132 & 289 & 0 \\
							& unsat    &   287*   &   211* &   100 &    111*  & 82 & 2 & 1 \\
							& $\times$ &   185*   &   174* &   481 &    451*  & 386 & 309 & 599 \\ \hline
\multirow{3}{*}{LeetCode}	& sat      &   856*   &   860* &   881 &    670*  & 778 & 0 & 158 \\
							& unsat    &  1784*   &  1785* &  1785 &   1780*  & 1827 & 0 & 1618 \\
							& $\times$ &    26*   &    21* &     0 &    216*  & 61 & 2666 & 890 \\ \hline
\multirow{3}{*}{StringFuzz}	& sat      &   502*   &   677* &   311 &    493*  & 688 & 439 & 0 \\
							& unsat    &   294*   &   240* &   205 &    190*  & 339 & 158 & 0 \\
							& $\times$ &   269*   &   148* &   549 &    382*  & 38 & 468 & 1065 \\\hline
\multirow{3}{*}{cvc4\textsubscript{pred}} & sat & 16* & 11* &   12 &      8*  & 247 & 316 & 21 \\
							& unsat    &   814*   &   818* &   808 &    772*  & 500 & 443 & 17 \\
							& $\times$ &     5*   &     6* &    15 &     55*  & 88 & 76 & 797 \\ \hline
\multirow{3}{*}{cvc4\textsubscript{term}} & sat & 13* & 8* &     6 &     16*  & 311 & 576 & 45 \\
							& unsat    &  1030*   &   936* &  1022 &    958*  & 596 & 349 & 22 \\
							& $\times$ &     2*   &   101* &    17 &     71*  & 137 & 120 & 978 \\ \hline
\multirow{3}{*}{SLOG}  		& sat      & 0* & 1309* & 0 & 0* & 1228 & 1036 & 1299 \\
							& unsat    & 3391* & 2082* & 0 & 2205* & 2079 & 1972 & 2079 \\
							& $\times$ & 0* & 0* & 3391 & 1186* & 84 & 383 & 13 \\ \hline
							\hline
\multirow{3}{*}{Total}  		& sat      & 0* & 1309* & 0 & 0* & 1228 & 1036 & 1299 \\
& unsat    & 3391* & 2082* & 0 & 2205* & 2079 & 1972 & 2079 \\
& $\times$ & 0* & 0* & 3391 & 1186* & 84 & 383 & 13 \\\hline
\end{tabular}}
\label{table:base_benchmark}
\end{table}

\begin{table}[h]
\centering
\caption{Results of {\tool}, CVC4, and Z3 on Basic String Constraints + String-Number Conversion benchmark (numbers with * will be updated later)}
\scalebox{0.8}{
\begin{tabular}{|l r | r r r r|}
\hline
\multicolumn{2}{|c}{}                   & {\tool} & CVC4   &    Z3  & Z3-str3 \\ \hline
\multirow{3}{*}{String-Number-Leetcode}		& sat      &   3294*  &  2185* &  2731* &    422* \\ 
							& unsat    &  17088*  & 16377* & 16832* &  16034* \\
							& $\times$ &   1191*  &  3011* &  2010* &   5117* \\ \hline 
\multirow{3}{*}{String-Number-PythonLib}		& sat      &   3294*  &  2185* &  2731* &    422* \\ 
& unsat    &  17088*  & 16377* & 16832* &  16034* \\
& $\times$ &   1191*  &  3011* &  2010* &   5117* \\ \hline
\multirow{3}{*}{String-Number-JavaScript}		& sat      &   3294*  &  2185* &  2731* &    422* \\ 
& unsat    &  17088*  & 16377* & 16832* &  16034* \\
& $\times$ &   1191*  &  3011* &  2010* &   5117* \\ \hline 							
							\hline
\multirow{3}{*}{Total}	& sat & 622*  &  330* &  100* &  85* \\ 
& unsat    &  1054*  & 780* & 1043* &  634* \\
& $\times$ &  2*  &  568* &  535* & 959* \\ \hline
\end{tabular}}
\label{table:str_int_benchmark}
\end{table}

\hide{%3rd version
\begin{table}[t]
	\centering
	\caption{Results of {\tool}, cvc4, and z3 on str\_int benchmark (numbers with * will be updated later)}
	\scalebox{0.7}{
		\begin{tabular}{l r | r r r r}
			\hline
			\multicolumn{2}{c}{}                   & {\tool} & CVC4   &    Z3  & Z3-str3 \\ \hline
			\multirow{3}{*}{String-Number}		& sat      &   3294*  &  2185* &  2731* &    422* \\ 
			& unsat    &  17088*  & 16377* & 16832* &  16034* \\
			& $\times$ &   1191*  &  3011* &  2010* &   5117* \\ \hline \hline

@@

\hide{  % 1st version of tables
\begin{table*}[t]
\centering
\caption{Results of {\tool}, cvc4, and z3 on string benchmarks}
\begin{tabular}{l | r r r | r r r | r r r | r r r}
\hline
\multirow{2}{*}{}   & \multicolumn{3}{|c|}{z3-Trau} & \multicolumn{3}{|c}{cvc4} & \multicolumn{3}{|c}{z3} & \multicolumn{3}{|c}{z3-str3} \\
			& sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ \\ \hline
PyEx		& 19586 & 3858 & 1969/8 & 19763 & 3834 & 0/1824 & 16581 & 3832 & 5008/0 & 3024 & 3839 & 16708/1850 \\ 
APLAS		&   128 &  287 &  185/0 & 205 &  221 & 174/0 &  13 &  100 & 486/1 & 38 & 111 & 93/358 \\ 
LeetCode	&   856 & 1784 &   26/0 & 860 & 1785 &  21/0 & 881 & 1785 & 0/0 & 670 & 1780 &  83/133 \\ 
StringFuzz	& 502 & 294 & 267/2 & 677 & 240 & 63/85 & 265 & 187 & 609/4 & 493 & 190 & 377/5 \\ 
cvc4\textsubscript{pred}	& 16 & 814 & 5/0 & 11 & 818 & 6/0 & 12 & 808 & 15/0 & 8 & 772 & 41/14 \\ 
cvc4\textsubscript{term}	& 13 & 1030 & 2/0 & 8 & 936 & 12/89 & 5 & 1021 & 19/0 & 16 & 958 & 53/18 \\ \hline
\end{tabular}
\label{table:base_benchmark}
\end{table*}
}

\hide{
\begin{table*}[t]
\centering
\caption{Results of z3-Trau, cvc4, and z3 on str\_int benchmark}
\begin{tabular}{l | r r r | r r r | r r r | r r r}
\hline
\multirow{2}{*}{}   & \multicolumn{3}{|c|}{z3-Trau} & \multicolumn{3}{|c}{cvc4} & \multicolumn{3}{|c}{z3} & \multicolumn{3}{|c}{z3-str3} \\
			& sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ \\ \hline
full\_str\_int		& 3294 & 17088 & 1191/0 & 2185 & 16377 & 3011/0 & 422 & 16034 & 4131/986 & 2731 & 16832 & 2010/0 \\ 
filtered\_str\_int	& 3281 & 2912 & 1203/0 & 2210 & 2211 & 2975/0 & 2729 & 2655 & 2012/0 & 424 & 1944 & 4106/922 \\ \hline
\end{tabular}
\label{table:str_int_benchmark}
\end{table*}
}

@@

We compare {\tool} with other state-of-the-art string solvers, namely CVC4~\cite{cvc4Tool}, Z3~\cite{z3}, \textsf{Z3-str3}~\cite{zheng2013z3}, \textsf{Trau+}~\cite{parosh2019chain}, , and Ostrich~\cite{chen2019decision}. We do not compare with Sloth \cite{sloth} since it does not support length constraints, which occurs in most of our benchmarks. We also do not compare with ABC~\cite{aydin2018parameterized} (a model counter for string constraints), which over-approximates cases that cannot be modeled by \emph{aligned multi-track automata}~\cite{yu2016optimal} and hence cannot solve our benchmark examples precisely.

>>>>

\begin{table}[h]
\centering
\caption{Results of {\tool}, CVC4, and Z3 on Basic String Constraint benchmarks.}
\scalebox{0.85}{
\begin{tabular}{|l r | r r r r r|}
\hline
\multicolumn{2}{|c}{}                   & {\tool} & CVC4  &Z3 & Z3-str3 & Trau+  \\ \hline
\multirow{3}{*}{PyEx}		& SAT      & 19586*   & 20123 & 18490 &  3514 & 19149 \\ 
							& UNSAT    &  3858*   &  3841 &  3855 &  4521 & 3828 \\
							& $\times$ &  1977*   &  1457 &  3076 & 17386 & 2444 \\ \hline
\multirow{3}{*}{APLAS}		& SAT      &   128*   &    51 &    19 &    52 & 132 \\
							& UNSAT    &   287*   &   214 &   100 &   118 & 82 \\
							& $\times$ &   185*   &   335 &   481 &   430 & 386 \\ \hline
\multirow{3}{*}{LeetCode}	& SAT      &   856*   &   871 &   881 &   651 & 778 \\
							& UNSAT    &  1784*   &  1785 &  1785 &  1787 & 1827 \\
							& $\times$ &    26*   &    10 &     0 &   228 & 61 \\ \hline
\multirow{3}{*}{StringFuzz}	& SAT      &   502*   &   610 &   316 &   605 & 688 \\
							& UNSAT    &   294*   &   255 &   206 &   217 & 339 \\
							& $\times$ &   269*   &   200 &   543 &   243 & 38 \\\hline
\multirow{3}{*}{cvc4\textsubscript{pred}} & SAT & 16* & 11 &   12 &    10 & 247 \\
							& UNSAT    &   814*   &   818 &   807 &   778 & 500 \\
							& $\times$ &     5*   &     6 &    16 &    47 & 88 \\ \hline
\multirow{3}{*}{cvc4\textsubscript{term}} & SAT & 13* & 9 &     6 &    16 & 311 \\
							& UNSAT    &  1030*   &  1025 &  1020 &   962 & 596 \\
							& $\times$ &     2*   &    11 &    19 &    67 & 138 \\ \hline
\multirow{3}{*}{Total} 		& SAT      & 21101*  &  21675 & 19724 &  4848 & 21305  \\
							& UNSAT    &  8067*  &   7938 &  7773 &  8383 & 7172  \\
							& $\times$ &  2464*  &  2019 &   4135 & 18401 & 3155  \\\hline	
\end{tabular}}
\label{table:base_benchmark}
\end{table}

\begin{table}[h]
\centering
\caption{Results of {\tool}, CVC4, and Z3 on Basic String Constraints + String-Number Conversion benchmark.}
\scalebox{0.8}{
\begin{tabular}{|l r | r r r r|}
\hline
\multicolumn{2}{|c}{}                   			& {\tool} & CVC4   &    Z3  & Z3-str3 \\ \hline
\multirow{3}{*}{String-Number-Leetcode}	 & SAT      &   2356*  &  1766 &  1025  &   333 \\ 
										 & UNSAT    &  16369*  & 15612 & 17234  & 15543 \\
										 & $\times$ &    202*  &  1549 &   668  &  3051 \\ \hline 
\multirow{3}{*}{String-Number-PythonLib} & SAT      &    912*  &   586 &  1802  &   389 \\ 
										 & UNSAT    &    720*  &   666 &   744  &   729 \\
										 & $\times$ &   1014*  &  1394 &   100  &  1528 \\ \hline
\multirow{3}{*}{String-Number-JavaScript}& SAT      &     20   &     5 &    16  &     4 \\ 
										 & UNSAT    &      0   &     0 &     0  &     0 \\
										 & $\times$ &      0   &    15 &     4  &    16 \\ \hline \hline
\multirow{3}{*}{Total}					 & SAT      &   3288*  &  2357 &  2843  &   726 \\ 
										 & UNSAT    &  17089*  & 16278 & 17978  & 16272 \\
										 & $\times$ &   1216*  &  2958 &   772  &  4595 \\ \hline
\end{tabular}}
\label{table:str_int_benchmark}
\end{table}

\begin{figure}
\begin{tikzpicture}
\begin{axis}
\addplot+[sharp plot]
coordinates
{
(2,0.097)
(3,0.078)
(4,0.098)
(5,0.098)
(6,0.161)
(7,0.236)
(8,0.307)
(9,0.26)
(10,0.211)
(11,0.228)
(12,0.33)
};
\end{axis}
\end{tikzpicture}
\caption{checkLuhn: z3-trau}
\end{figure}

\begin{figure}
\begin{tikzpicture}
\begin{axis}
\addplot+[sharp plot]
coordinates
{
(2,0.266)
(3,10.084)
(4,48.791)
(5,120)
(6,120)
(7,120)
(8,120)
(9,120)
(10,120)
(11,120)
(12,120)
};
\end{axis}
\end{tikzpicture}
\caption{checkLuhn: cvc4 (SAT if not timeout)}
\end{figure}

\begin{figure}
\begin{tikzpicture}
\begin{axis}
\addplot+[sharp plot]
coordinates
{
(2,0.238)
(3,0.128)
(4,120)
(5,120)
(6,0.134)
(7,120)
(8,0.366)
(9,120)
(10,0.526)
(11,0.374)
(12,0.405)
};
\end{axis}
\end{tikzpicture}
\caption{checkLuhn: z3 (SAT if not timeout)}
\end{figure}

\begin{figure}
\begin{tikzpicture}
\begin{axis}
\addplot+[sharp plot]
coordinates
{
(2,0.4743)
(3,0.56052)
(4,0.36695)
(5,0.60905)
(6,22.06429)
(7,53.77536)
(8,118.41196)
(9,0.50559)
(10,120)
(11,0.42953)
(12,120)
};
\end{axis}
\end{tikzpicture}
\caption{checkLuhn: z3str3 (UNKNOWN if not timeout)}
\end{figure}

\hide{ % keep data of abc and ostrich
\begin{table}[h]
\centering
\caption{Results of Z3-Trau, CVC4, and Z3 on Basic String Constraint benchmarks (numbers with * will be updated later)}
\scalebox{0.7}{
\begin{tabular}{|l r | r r r r r r r|}
\hline
\multicolumn{2}{|c}{}                   & {\tool} & CVC4  &Z3 & Z3-str3 & Trau+ & ABC & Ostrich \\ \hline
\multirow{3}{*}{PyEx}		& sat      & 19586*   & 19763* & 18490 &   3024*  & 19149 & 0 & 111 \\ 
							& unsat    &  3858*   &  3834* &  3855 &   3839*  & 3828 & 0 & 871 \\
							& $\times$ &  1977*   &  1824* &  3076 &  18558*  & 2444 & 25421 & 24439 \\ \hline
\multirow{3}{*}{APLAS}		& sat      &   128*   &   205* &    19 &     38*  & 132 & 289 & 0 \\
							& unsat    &   287*   &   211* &   100 &    111*  & 82 & 2 & 1 \\
							& $\times$ &   185*   &   174* &   481 &    451*  & 386 & 309 & 599 \\ \hline
\multirow{3}{*}{LeetCode}	& sat      &   856*   &   860* &   881 &    670*  & 778 & 0 & 158 \\
							& unsat    &  1784*   &  1785* &  1785 &   1780*  & 1827 & 0 & 1618 \\
							& $\times$ &    26*   &    21* &     0 &    216*  & 61 & 2666 & 890 \\ \hline
\multirow{3}{*}{StringFuzz}	& sat      &   502*   &   677* &   316 &    493*  & 688 & 439 & 0 \\
							& unsat    &   294*   &   240* &   206 &    190*  & 339 & 158 & 0 \\
							& $\times$ &   269*   &   148* &   543 &    382*  & 38 & 468 & 1065 \\\hline
\multirow{3}{*}{cvc4\textsubscript{pred}} & sat & 16* & 11* &   12 &      8*  & 247 & 316 & 21 \\
							& unsat    &   814*   &   818* &   807 &    772*  & 500 & 443 & 17 \\
							& $\times$ &     5*   &     6* &    16 &     55*  & 88 & 76 & 797 \\ \hline
\multirow{3}{*}{cvc4\textsubscript{term}} & sat & 13* & 8* &     6 &     16*  & 311 & 576 & 45 \\
							& unsat    &  1030*   &   936* &  1020 &    958*  & 596 & 349 & 22 \\
							& $\times$ &     2*   &   101* &    19 &     71*  & 137 & 120 & 978 \\ \hline
\multirow{3}{*}{SLOG}  		& sat      & 0* & 1309* & 0 & 0* & 1228 & 1036 & 1299 \\
							& unsat    & 3391* & 2082* & 2824 & 2205* & 2079 & 1972 & 2079 \\
							& $\times$ & 0* & 0* & 567 & 1186* & 84 & 383 & 13 \\ \hline \hline
\multirow{3}{*}{Total} 		& sat      & * & * & 19724 & * &  &  &  \\
							& unsat    & * & * & 10597 & * &  &  &  \\
							& $\times$ & * & * &  4702 & * &  &  &  \\\hline
\end{tabular}}
\label{table:base_benchmark}
\end{table}
}

\hide{ %3rd version of tables
\begin{table}[t]
	\centering
	\caption{Results of {\tool}, cvc4, and z3 on str\_int benchmark (numbers with * will be updated later)}
	\scalebox{0.7}{
		\begin{tabular}{l r | r r r r}
			\hline
			\multicolumn{2}{c}{}                   & {\tool} & CVC4   &    Z3  & Z3-str3 \\ \hline
			\multirow{3}{*}{String-Number}		& sat      &   3294*  &  2185* &  2731* &    422* \\ 
			& unsat    &  17088*  & 16377* & 16832* &  16034* \\
			& $\times$ &   1191*  &  3011* &  2010* &   5117* \\ \hline \hline

@@

\hide{  % 1st version of tables
\begin{table*}[t]
\centering
\caption{Results of {\tool}, cvc4, and z3 on string benchmarks}
\begin{tabular}{l | r r r | r r r | r r r | r r r}
\hline
\multirow{2}{*}{}   & \multicolumn{3}{|c|}{z3-Trau} & \multicolumn{3}{|c}{cvc4} & \multicolumn{3}{|c}{z3} & \multicolumn{3}{|c}{z3-str3} \\
			& sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ \\ \hline
PyEx		& 19586 & 3858 & 1969/8 & 19763 & 3834 & 0/1824 & 16581 & 3832 & 5008/0 & 3024 & 3839 & 16708/1850 \\ 
APLAS		&   128 &  287 &  185/0 & 205 &  221 & 174/0 &  13 &  100 & 486/1 & 38 & 111 & 93/358 \\ 
LeetCode	&   856 & 1784 &   26/0 & 860 & 1785 &  21/0 & 881 & 1785 & 0/0 & 670 & 1780 &  83/133 \\ 
StringFuzz	& 502 & 294 & 267/2 & 677 & 240 & 63/85 & 265 & 187 & 609/4 & 493 & 190 & 377/5 \\ 
cvc4\textsubscript{pred}	& 16 & 814 & 5/0 & 11 & 818 & 6/0 & 12 & 808 & 15/0 & 8 & 772 & 41/14 \\ 
cvc4\textsubscript{term}	& 13 & 1030 & 2/0 & 8 & 936 & 12/89 & 5 & 1021 & 19/0 & 16 & 958 & 53/18 \\ \hline
\end{tabular}
\label{table:base_benchmark}
\end{table*}

\begin{table*}[t]
\centering
\caption{Results of z3-Trau, cvc4, and z3 on str\_int benchmark}
\begin{tabular}{l | r r r | r r r | r r r | r r r}
\hline
\multirow{2}{*}{}   & \multicolumn{3}{|c|}{z3-Trau} & \multicolumn{3}{|c}{cvc4} & \multicolumn{3}{|c}{z3} & \multicolumn{3}{|c}{z3-str3} \\
			& sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ \\ \hline
full\_str\_int		& 3294 & 17088 & 1191/0 & 2185 & 16377 & 3011/0 & 422 & 16034 & 4131/986 & 2731 & 16832 & 2010/0 \\ 
filtered\_str\_int	& 3281 & 2912 & 1203/0 & 2210 & 2211 & 2975/0 & 2729 & 2655 & 2012/0 & 424 & 1944 & 4106/922 \\ \hline
\end{tabular}
\label{table:str_int_benchmark}
\end{table*}
}

@@

We compare {\tool} with other state-of-the-art string solvers, namely CVC4(Relese-1.7)~\cite{cvc4Tool}, Z3(master:dde8da853)~\cite{z3}, \textsf{Z3-str3}(master:109dfc5e8)~\cite{zheng2013z3}, \textsf{Trau+}~\cite{parosh2019chain}, , and Ostrich~\cite{chen2019decision}. We do not compare with Sloth \cite{sloth} since it does not support length constraints, which occurs in most of our benchmarks. We also do not compare with ABC~\cite{aydin2018parameterized} (a model counter for string constraints), which over-approximates cases that cannot be modeled by \emph{aligned multi-track automata}~\cite{yu2016optimal} and hence cannot solve our benchmark examples precisely.
